---
title: "simpleRegress"
author: "Sisilia Martinez"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

When comparing length to weight the adjusted R^2 was less than the adjusted R^2 when comparing length and neck size. Which is why using the neck size to help predict length was better than using weight.

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

Predicting length with head length the adjusted R^2 was larger than when we predicted length with neck size. The residual standard error for head length is less than that of the neck size prediction. Which is why predicting length with head length is a better comparison than using neck size to determine length.

```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

Using age to predict length was worse than using neck to predict length. This is because of the adjusted R^2 was smaller when predicting length with age and the residual standard error was larger. 

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

Using head width to predict length was worse than using neck to predict length. This is because the adjusted R^2 was smaller when predicting length with head width and residual standard error was larger. 
